Improved Approximation Algorithms for the Maximum Carpool Matching Problme

### 2017-02-09 src/sub.tex
rm todos

\begin{figure}
\centering
\input{fig-submodular}
\caption[]{
\label{fig:defs}
We show that the arcs from \subref{sub:cup} and \subref{sub:cap} can be
redistributed over \subref{sub:s} and \subref{sub:s} \todo{write explanation}}
\end{figure}

>>>>

\begin{figure}
\centering
\input{fig-submodular}
\caption[]{
\label{fig:defs}
We show that the arcs from \subref{sub:cup} and \subref{sub:cap} can be
redistributed over \subref{sub:s} and \subref{sub:s} 
%\todo{write explanation}
}
\end{figure}
